Import OLIS spectral data

### 2023-12-07 Code/JazDataImport.Rmd
Changed folder names and paths to align with Sylwia

DataIn <- file.path("..", "Data","RawData", "MCEmissionSpectra", fsep = .Platform$file.sep)

DataOut<- file.path("..", "Data", "ProcessedData", fsep = .Platform$file.sep)

>>>>

DataIn <- file.path("..", "Data","RawData", "JazEm", fsep = .Platform$file.sep)

DataOut<- file.path("..", "Data", "ImportedData", "ImportedJazEmData", fsep = .Platform$file.sep)

### 2023-12-07 Code/MultiDataImportPico.Rmd
Changed folder names and paths to align with Sylwia

# Set Project Variables
```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "RawData", "MultiCultiData.zip")
DataOut <- file.path("..","Data", "ImportedData", "MultiCultiData")

>>>>

# Set Project Variables
```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "RawData", "MultiCultiData.zip")
DataOut <- file.path("..","Data", "ImportedData", "ImportedMCData")

### 2023-12-07 Code/MultiDataProcessPico.Rmd
Changed folder names and paths to align with Sylwia

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "ImportedData", "MultiCultiData")
DataOut <- file.path("..", "Data","ProcessedData", "MultiCultiData")

>>>>

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "ImportedData", "ImportedMCData")
DataOut <- file.path("..", "Data","ProcessedData", "ProcessedMCData")

### 2023-12-07 Code/OlisImportPurCalc.Rmd
Changed DataOut path
Changed folder names and paths to align with Sylwia

DataInSpectra <- file.path("..", "Data", "ProcessedData",  fsep = .Platform$file.sep)

DataInPAR <- file.path("..", "Data","RawData","MCEmissionSpectra", fsep = .Platform$file.sep)

DataOut <- file.path("..", "Data", "ProcessedData","MultiCultiEmissionData")

>>>>

DataInSpectra <- file.path("..", "Data", "ImportedData","ImportedJazEmData",  fsep = .Platform$file.sep)

DataInPAR <- file.path("..", "Data","RawData","JazEm", fsep = .Platform$file.sep)

DataOut <- file.path("..", "Data", "ImportedData","ImportedOlisData")
